Modelling the Lymphatic Metastatic Progression Pathways of OPSCC from Multi-Institutional Datasets

### 2023-01-06 src/tex/ms.tex
[showyourwork] overleaf sync

@@

We have more freedom in choosing how to connect the \glspl{lnl} to each other.

@@

\begin{figure}
    \centering
    \includegraphics{figures/extended_graph.png}
    \caption{Extended \gls{dag} representing different possible spread graphs underlying the \gls{hmm}. As in \cref{fig:graph_with_obs}, red arcs are parametrized with probabilities of spread from the tumor (red circle) to the \glspl{lnl} (blue circles). These red arcs, together with the blue arcs fron \gls{lnl} to \gls{lnl}, make up the \emph{base graph}. One after the other, each of the green arcs was added to the base graph. Subsequently, the performance of the resulting models in terms of its \gls{bic} was compared to the base graph to asssess whether the additional edge should be kept in the \emph{winning graph} or not.}
    \label{fig:extended_graph}
\end{figure}

@@

\begin{figure}
    \script{comp_IIandVII_prevs.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/comp_IIandVII_prevs.png}
        \caption{Prevalences for involvement patterns where \gls{lnl} VII is involved with (red) and without (blue) \gls{lnl} II. The solid lines depict a Beta posterior over the prevalence as observed in the data. The colored histograms show these prevalences as predicted by the winning graph. The hatched histograms show the same predictions from the base graph for comparison. Since the winning graph does not include an additional arc between \glspl{lnl} II and VII, the fit w.r.t. these two \glspl{LNL} does not improve.}
        \label{fig:IIandVII_prevs}
    \end{centering}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=0.6\linewidth]{figures/extended_graph.png}
    \caption{Extended \gls{dag} representing different possible spread graphs underlying the \gls{hmm}. As in \cref{fig:graph_with_obs}, red arcs are parametrized with probabilities of spread from the tumor (red circle) to the \glspl{lnl} (blue circles). These red arcs, together with the blue arcs fron \gls{lnl} to \gls{lnl}, make up the \emph{base graph}. One after the other, each of the green arcs was added to the base graph. Subsequently, the performance of the resulting models in terms of its \gls{bic} was compared to the base graph to asssess whether the additional edge should be kept in the \emph{winning graph} or not.}
    \label{fig:extended_graph}
\end{figure}

@@

We have more freedom in choosing how to connect the \glspl{lnl} to each other. To investigate which connections to add we start by establishing a baseline from a model using a minimal \emph{base graph}. It contains only the connections from \gls{lnl} II to III and an arc from \gls{lnl} III to IV, as motivated by the \emph{main lymphatic pathway} \cite{lengele_anatomical_2007}. In contrast to the \gls{dag} used in \cite{pouymayou_bayesian_2019,ludwig_hidden_2021}, we decided not to include the edge from level I to II into the base graph, since \gls{lnl} I is rarely involved and inferring $t_{12}$ is therefore difficult. Rather, we wanted to use the model comparison methodology outlined in \cref{subsec:methods:comparison} to see if the arc from \gls{lnl} I to II can be motivated from our data of if the arc should be flipped and go from \gls{lnl} II to I.

@@

@@

\begin{figure}
    \script{comp_IIandVII_prevs.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/comp_IIandVII_prevs.png}
        \caption{Prevalences for involvement patterns where \gls{lnl} VII is involved with (red) and without (blue) \gls{lnl} II. The solid lines depict a Beta posterior over the prevalence as observed in the data. The colored histograms show these prevalences as predicted by the winning graph. The hatched histograms show the same predictions from the base graph for comparison. Since the winning graph does not include an additional arc between \glspl{lnl} II and VII, the fit w.r.t. these two \glspl{lnl} does not improve.}
        \label{fig:IIandVII_prevs}
    \end{centering}
\end{figure}
